---
title: "05-exercises"
author: "Your Name Here"
date: "2016-05-xx"
output: html_document
---
  
  ## Reading:
  - **APM** Chapter 8.1-8.5 "Regression Trees and Rule-Based Models" (25 pages)
- **APM** Chapter 14.1-14.5 "Classification Trees and Rule-Based"  

```{r, echo=FALSE, results='hide', warning=FALSE }
packs <-  c('ggplot2', 'magrittr', 'dplyr', 'caret', 'AppliedPredictiveModeling', 'MASS' , 'maptree' , 'pROC')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

.. = NULL  # For Aesthetics

```


## Exercise 1: GermanCredit

Revisit the GermanCredit data. Use `caret` to build models of `Class` using the following techniques:
  
  - glm
- rpart
- knn
- party::ctree
- randomForest
- A method of your choice from the Caret Model List (you will need to install any dependencies)

Save the caret objects with the names provided.

```{r}

data("GermanCredit")
gc <- GermanCredit

ctrl <- trainControl( method="boot", number=5
                      , classProb=TRUE, savePrediction=TRUE )


# Your work here. 

set.seed(1234)
fit.glm <- train(Class ~ ., data=gc, method="glm", family="binomial", trControl=ctrl)
set.seed(1234)
fit.knn <- train( Class ~ ., data=gc, trControl=ctrl
              , method="knn", tuneGrid=data.frame( k=c(40,50,60)))
set.seed(1234)
fit.rpart <- train( Class ~ ., data=gc, trControl=ctrl
              , method="rpart", tuneLength=20) 
set.seed(1234)
fit.rf <- train( Class ~ ., data=gc, trControl=ctrl
              , method="rf") 
set.seed(1234)
fit.gbm <- train( Class ~ ., data=gc, trControl=ctrl
              , method="gbm")


````


- Compare the models using `caret::confusionMatrix`
- Comparing the models Using the `pROC` packages
- create ROC curves for the models 

Show your work! 

```{r}
cat('GLM')
table(fit.glm$pred$pred, fit.glm$pred$obs) %>% confusionMatrix()
roc <- roc(fit.glm$pred$obs, fit.glm$pred$Bad, auc=TRUE )
roc %>% plot( print.auc=TRUE, grid=TRUE)

cat('Knn')
table(fit.knn$pred$pred, fit.knn$pred$obs) %>% confusionMatrix()
roc <- roc(fit.knn$pred$obs, fit.knn$pred$Bad, auc=TRUE )
roc %>% plot( print.auc=TRUE, grid=TRUE)

cat('rPart')
table(fit.rpart$pred$pred, fit.rpart$pred$obs) %>% confusionMatrix()
roc <- roc(fit.rpart$pred$obs, fit.rpart$pred$Bad, auc=TRUE )
roc %>% plot( print.auc=TRUE, grid=TRUE)

cat('Random Forest')
table(fit.rf$pred$pred, fit.rf$pred$obs) %>% confusionMatrix()
roc <- roc(fit.rf$pred$obs, fit.rf$pred$Bad, auc=TRUE )
roc %>% plot( print.auc=TRUE, grid=TRUE)

cat('GBM')
table(fit.gbm$pred$pred, fit.gbm$pred$obs) %>% confusionMatrix()
roc <- roc(fit.gbm$pred$obs, fit.gbm$pred$Bad, auc=TRUE )
roc %>% plot( print.auc=TRUE, grid=TRUE)






```


Q: Which models would you select based on these tools?

###As shown in the results, GLM model has the highest accuracy and AUC that looks the champion. 

Q: If you assume that a `Class=="bad""` is 10 more costly than `Class=="good"`, determine your threshold for the model of your choice.  Show your work.


```{r}

roc <- roc(fit.glm$pred$obs, fit.glm$pred$Bad, auc=TRUE )
res<-coords(roc, "b", ret="t", best.method="youden", best.weights=c(10, 0.3))
cat('The optiml threshold is: ', res)

```

